Verifying synchronous distributed algorithms using IVy

### 2018-08-06 paper/paper.tex
- page 9, section (IV.i): I would add an introductory paragraph for the 	section "Modeling strategy", and state that the remainder of the section 	contains some challenges that came across while using IVy, and how they were 	overcome

The goal of this section is to walk through the specification step by step, to illustrate the paradigms relevant to automatic verification in IVy. The complete code, together with setup instructions of a Docker container, can be found here \cite{github}.

@@

>>>>

@@

This section walks through the specification step by step. It illustrates the paradigms relevant to verification in IVy and presents the challenges that the author came across while specifying in IVy, and how they were overcome. The complete code, together with setup instructions of a Docker container, can be found here \cite{github}.
